Lessons learned from bugs in models of human history

### 2020-05-20 paper.tex
title edits

\title{Describing demographic models is hard}
\author[1]{Aaron P. Ragsdale}
\author[1]{Dominic Nelson}
\author[1,$\star$]{Simon Gravel}
\author[2,$\star$]{Jerome Kelleher}
\affil[1]{McGill University and Genome Qu\'{e}bec Innovation Centre,
McGill University, Montr\'{e}al, Qu\'{e}bec, Canada}
\affil[2]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery,
University of Oxford, Oxford, United Kingdom}
\affil[$\star$]{Joint senior authors, listed alphabetically}
\maketitle

\aprcomment{title thoughts: \\
Reducing errors in demographic model design and implementation \\
}

@@

\section{Introduction}

@@

\section{A bad tutorial example}

@@

Fortunately, the effects of this error are subtle.
Population sizes and structure since the time of
the split are unaffected, so that differences in expected $F_{ST}$ are negligible between
the correct and incorrect model. However, the ancient structure distorts the distribution
of early $T_{MRCAs}$. The extraneous ancient population increases increases the long-term effective 
population size, leading to heterozygosity in contemporary populations
increased by roughly $4\%$ over expectations from the correctly specified 
model (Fig.~\ref{fig:ooa_stats}E-F).

@@

\section{Risk prediction in human populations}

@@

\section{Conclusions}

@@

\section{Methods}

>>>>

\title{Lessons learned from bugs in models of human history}
\author[1]{Aaron P. Ragsdale}
\author[1]{Dominic Nelson}
\author[1,$\star$]{Simon Gravel}
\author[2,$\star$]{Jerome Kelleher}
\affil[1]{McGill University and Genome Qu\'{e}bec Innovation Centre,
McGill University, Montr\'{e}al, Qu\'{e}bec, Canada}
\affil[2]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery,
University of Oxford, Oxford, United Kingdom}
\affil[$\star$]{Joint senior authors, listed alphabetically}
\maketitle

\aprcomment{title thoughts: \\
Reducing errors in demographic model design and implementation \\
}
\sgcomment{How to avoid simulating the wrong demographic model}

@@

\section*{Introduction}

@@

\section*{Case 1: A misspecified model in msprime's documentation}

@@

Fortunately, the effects of this error are subtle.
Population sizes and structure since the time of
the split are unaffected, so that differences in expected $F_{ST}$ are negligible between
the correct and incorrect model. However, the ancient structure distorts the distribution
of early $T_{MRCAs}$. The extraneous ancient population increases the long-term effective 
population size, leading to heterozygosity in contemporary populations
increased by roughly $4\%$ over expectations from the correctly specified 
model (Fig.~\ref{fig:ooa_stats}E-F).

@@

\section*{Case 2: Incorrect model parameters in an analysis pipeline}

@@

\section*{Conclusions}

@@

\section*{Methods}
